%-------------------------
% Resume in LaTeX
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\usepackage{amsfonts}
\usepackage{amssymb}
\IfFileExists{fontawesome5.sty}{\usepackage{fontawesome5}}{}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable / ATS parseable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \hspace{12pt}#2 \\
      \textit{\small#3} & \hspace{12pt}\textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \hspace{8pt}\small#2 \\
    \end{tabular*}\vspace{-11pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[nosep, itemsep=1pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\setlength{\parskip}{0pt}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Prathamesh Vaze} \\ \vspace{4pt}
    \small
    \fontsize{9}{11}\selectfont
    \href{mailto:prathameshvaze@gmail.com}{\underline{prathameshvaze@gmail.com}} ~$|$~
    \href{tel:+919403329930}{\underline{+91 9403329930}} ~$|$~
    \href{https://www.linkedin.com/in/prathameshvaze/}{\underline{linkedin.com/in/prathameshvaze}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      Laravel Backend Developer with 3+ years building secure, scalable applications and APIs. Specializing in performance tuning, codebase modernization, and seamless third-party integrations. Contributor to Laravel open-source projects and community events like Laracon and Laravel Mumbai. Familiar with AI-powered development tools and automation workflows; actively exploring applications of AI in backend development and API security.
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {12Grids --- The CX Technology Company}{Jan 2024 -- Present}
      {Software Engineer Innovator}{}
      \resumeItemListStart
        \resumeItem{Led design and strategy for system and database architecture to ensure scalability and maintainability.}
        \resumeItem{Automated 25\% of processes using CRON jobs, reducing manual efforts and boosting operational efficiency.}
        \resumeItem{Refactored and optimized codebase for improved performance and reliability.}
        \resumeItem{Oversaw task allocation and sprint planning across multiple ongoing projects.}
        \resumeItem{Leveraged AI-assisted code tools like GitHub Copilot and Cursor to accelerate feature development and improve code quality.}
      \resumeItemListEnd

    \resumeSubheading
      {12Grids --- The CX Technology Company}{Mar 2022 -- Dec 2023}
      {Software Engineer Innovator}{}
      \resumeItemListStart
        \resumeItem{Developed and maintained APIs for iOS and Android mobile apps to support a smooth and responsive user experience.}
        \resumeItem{Integrated middleware and rate limiting to enhance API security and performance.}
        \resumeItem{Spearheaded improvements in deployment pipelines, reducing deployment times by 70\%.}
        \resumeItem{Established long-term health and stability of projects through process improvements and documentation.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {S. R. M. College, Kudal}{}
      {B.Sc. Computer Science}{CGPA: 9.83}
    \resumeSubheading
      {N. A. D. Topiwalla Jr. College}{}
      {Higher Secondary Certificate (HSC)}{64\%}
    \resumeSubheading
      {A. S. D. Topiwalla High School}{}
      {Secondary School Certificate (SSC)}{78.6\%}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading{\textbf{\href{https://github.com/yourhandle/example-app}{example-app}} $|$ {\small $\bigstar$ 1k stars} \textnormal{ -- short one-line description of what it does and why it matters}}{}
      \resumeProjectHeading{\textbf{\href{https://github.com/yourhandle/another-tool}{another-tool}} \textnormal{ -- a CLI that does X for Y}}{}
      \resumeProjectHeading{\textbf{closed-source-thing} \textnormal{(closed source) -- internal project; describe scope, not internals}}{}
      \resumeProjectHeading{\textbf{learning-project} \textnormal{ -- built to learn N; one-liner about result}}{}
      \resumeProjectHeading{\textbf{landing-page-clone} \textnormal{ -- recreation of X landing page with modern stack}}{}
      \resumeProjectHeading{\textbf{api-wrapper} \textnormal{ -- minimal SDK around the X public API}}{}

    \resumeSubHeadingListEnd

%-----------OPEN SOURCE-----------
\section{Open Source Contributions}
    \resumeSubHeadingListStart

      \resumeProjectHeading{\textbf{\href{https://github.com/owner/popular-repo/pull/12345}{popular-repo}} $|$ {\small $\bigstar$ 100k stars} \textnormal{ -- fix: short one-line summary of the merged PR}}{}
      \resumeProjectHeading{\textbf{another-repo} $|$ {\small $\bigstar$ 10k stars} \textnormal{ -- feat: implement a small but useful improvement}}{}
      \resumeProjectHeading{\textbf{small-repo} $|$ {\small $\bigstar$ 500 stars} \textnormal{ -- docs: clarify usage section}}{}

    \resumeSubHeadingListEnd

%-----------HONORS & AWARDS-----------
\section{Honors \& Awards}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
       \textbf{Recent Award} -- short context (issuer, what it was for) & 2026 \\[0pt]
       \textbf{Dean's List} -- CGPA range, university name & Feb 2026 \\[0pt]
       \textbf{Hackathon Winner} -- event name, placement & 2025 \\[0pt]
       \textbf{Older Honor} -- one-line context & 2024 \\
     \end{tabular*}
    }}
 \end{itemize}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages \& Frameworks}{: PHP, Laravel, MySQL, ReactJS} \\
     \textbf{Databases \& Tools}{: TablePlus, MySQL Workbench, phpMyAdmin, Git, GitHub, GitLab, Postman, Telescope, Debugbar} \\
     \textbf{Deployment \& Cloud}{: Laravel Forge, Laravel Cloud, GitHub Actions, AWS, Azure, DigitalOcean} \\
     \textbf{AI Tools}{: Claude, ChatGPT, GitHub Copilot, Cursor, OpenAI API} \\
     \textbf{Editors}{: VS Code, PHPStorm, Cursor}
    }}
 \end{itemize}

%-----------CERTIFICATIONS & VOLUNTEERING-----------
\section{Certifications \& Volunteering}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item Active contributor at \textbf{Laravel Mumbai Community}.}
    \small{\item Event volunteer at \textbf{Laracon IN 2025} for coordination and engagement.}
 \end{itemize}

%-----------LANGUAGES & INTERESTS-----------
\section{Languages \& Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: English, Hindi, Marathi} \\
     \textbf{Interests}{: Chess, Cooking, Streaming, Reading}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
